### 2022-03-10 sections/simulated_samples.tex
updates for more comments
add new limit plots
update most comments

An overview of the MC generators used for the main signal and background samples is summarized in Table~\ref{mob}.

Samples of simulated $\ttbar \to WbHq$ ($tt(qH)$) events were generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix-element (ME) calculation 
is performed.} {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
%{\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering (PS), hadronisation, and the underlying event. 
The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
initial- and final-state radiation, referred to as the tune, was used.
The signal sample is normalised to the same total cross section as used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below) and
assuming a benchmark branching ratio of $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$.
The case of both top quarks decaying into $qH$ is neglected in the analysis given the existing upper limits on $\BR(t \to qH)$ (Section~\ref{sec:intro}).

@@

Samples of $WH$ and $ZH$, collectively referred to as $VH$ are generated using {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
and interfaced to {\pythia}~8.210 with the NNPDF2.3 LO PDF set and the A14 tune.
The contribution of $tH$ associated production is also considered as part of SM Higgs background.
The sample is generated using {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca} and interfaced with {\pythia}~8.210 with CT10PDF
and A14 tune. The MC predictions are normalised using the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.

All generated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
utilise \textsc{EvtGen}~1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
To model the effects of pile-up, events from minimum-bias interactions were generated using {\pythia}~8.186~\cite{Sjostrand:2007gs}  
in combination with the A2 tune~\cite{ATL-PHYS-PUB-2011-014}, 
and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 
The generated events were processed through a simulation~\cite{Aad:2010ah} of the ATLAS detector geometry and response 
using \textsc{Geant4}~\cite{Agostinelli:2002hh}. A faster simulation, where the full \textsc{Geant4} simulation of
the calorimeter response is replaced by a detailed parameterisation of the shower shapes~\cite{FastCaloSim},
was adopted for some of the samples used to estimate systematic uncertainties in background modelling.
Simulated events were processed through the same reconstruction software as the data, and corrections were applied so that the object identification 
efficiencies, energy scales and energy resolutions match those determined from data control samples.

\begin{table}
\footnotesize
\centering
\caption{Overview of the MC generators at which the matrix-element calculation (ME) at the leading or the next-leading order (Order), 
the parton shower model (PS), and the parton distribution function set (PDF) used for the main signal and background samples.}
\begin{tabular}[h]{l|c|c|c|c|c|c}
\hline \hline
\multirow{2}{*}{Process} & \multicolumn{2}{c|}{Generator} & \multicolumn{2}{c|}{PDF set} & \multirow{2}{*}{Tune} & \multirow{2}{*}{Order} \\ \cline{2-5}
        &  ME   &  PS    &  ME  & PS &   &  \\\hline
$tt(qH)$ Signal & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$tH$ Signal & {\amcatnlolong} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$W/Z$+jets & \multicolumn{2}{c|}{{\sherpa}~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & {\sherpa} & NLO/LO \\ \hline
\ttbar & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
Single top & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$t\bar{t}X$ & {\amcatnlolong} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
Diboson & \multicolumn{2}{c|}{{\sherpa}~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & {\sherpa} & NLO/LO \\ \hline\hline
\end{tabular}
\label{mob}
\end{table}

>>>>

An overview of the Monte Carlo (MC) generators used for the main signal and background samples is summarized in Table~\ref{mob}.
Samples of simulated $\ttbar \to WbHq$ ($tt(qH)$) events were generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix-element (ME) calculation 
is performed.} {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
%{\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering (PS), hadronisation, and the underlying event. 
The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
initial- and final-state radiation, referred to as the tune, was used.
The signal sample is normalised to the same total cross section as used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below) and
assuming a benchmark branching ratio of $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$.
The case of both top quarks decaying into $qH$ is neglected in the analysis given the existing upper limits on $\BR(t \to qH)$ (Section~\ref{sec:intro}).

@@

Samples of $WH$ and $ZH$, collectively referred to as $VH$ are generated using {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
and interfaced to {\pythia}~8.210 with the PDF4LHC15 PDF set and the AZNLO tune.
The contribution of $tH$ associated production is also considered as part of SM Higgs background.
The sample is generated using {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca} and interfaced with {\pythia}~8.210 with CT10PDF
and A14 tune. The MC predictions are normalised using the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.

All generated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
utilise \textsc{EvtGen}~1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
%To model the effects of pile-up, events from minimum-bias interactions were generated using {\pythia}~8.186~\cite{Sjostrand:2007gs}  
%in combination with the A3 tune~\cite{ATL-PHYS-PUB-2011-014}, 
The effects of multiple interactions in the same and nearby bunch crossings (pile-up) were modelled by overlaying minimum-bias events, simulated using the soft QCD processes of {\pythia}~8.186~\cite{Sjostrand:2006za} with the A3~\cite{ATL-PHYS-PUB-2016-017} set of tuned parameters and NNPDF2.3 LO PDF set~\cite{Ball:2012cx}.
%parton distribution functions (PDF).

%and overlaid onto the simulated hard-scatter events according to the luminosity profile of the recorded data. 
The generated events were processed through a simulation~\cite{Aad:2010ah} of the ATLAS detector geometry and response 
using \textsc{Geant4}~\cite{Agostinelli:2002hh}. A faster simulation, where the full \textsc{Geant4} simulation of
the calorimeter response is replaced by a detailed parameterisation of the shower shapes~\cite{FastCaloSim},
was adopted for some of the samples used to estimate systematic uncertainties in background modelling.
Simulated events were processed through the same reconstruction software as the data, and corrections were applied so that the object identification 
efficiencies, energy scales and energy resolutions match those determined from data control samples.

%  \begin{table}
%  \footnotesize
%  \centering
%  \caption{Overview of the MC generators used for the main signal and background samples.}
%  \begin{tabular}[h]{l|c|c|c|c|c|c}
%  \hline \hline
%  \multirow{2}{*}{Process} & \multicolumn{2}{c|}{Generator} & \multicolumn{2}{c|}{PDF set} & \multirow{2}{*}{Tune} & \multirow{2}{*}{Order} \\ \cline{2-5}
%          &  ME   &  PS    &   ME  & PS &   &  \\\hline
%  $tt(qH)$ Signal & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
%  $tH$ Signal & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
%  $W/Z$+jets & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline
%  \ttbar & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
%  Single top & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
%  $t\bar{t}X$ & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
%  Diboson & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline\hline
%  \end{tabular}
%  \label{mob}
%  \end{table}

\begin{table}
\footnotesize
\centering
\caption{Overview of the MC generators at which the matrix-element calculation (ME) at the leading or the next-leading order (Order), 
the parton shower model (PS), and the parton distribution function set (PDF) used for the main signal and background samples.}
\begin{tabular}[h]{l|c|c|c|c|c|c}
\hline \hline
\multirow{2}{*}{Process} & \multicolumn{2}{c|}{Generator} & \multicolumn{2}{c|}{PDF set} & \multirow{2}{*}{Tune} & \multirow{2}{*}{Order} \\ \cline{2-5}
        &  ME   &  PS    &  ME  & PS &   &  \\\hline
$tt(qH)$ Signal & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$tH$ Signal & {\amcatnlolong} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$W/Z$+jets & \multicolumn{2}{c|}{{\sherpa}~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & {\sherpa} & NLO/LO \\ \hline
\ttbar & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
Single top & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$t\bar{t}X$ & {\amcatnlolong} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline

%$VH$ & {\powheg} & {\pythia}~8 & \multicolumn{2}{c|}{PDF4LHC15} & AZNLO & NLO \\ \hline
$VH$ & {\powheg} & {\pythia}~8 & PDF4LHC15&CTEQ6L1 & AZNLO & NLO \\ \hline
$tH$ & {\amcatnlolong} & {\pythia}~8 & \multicolumn{2}{c|}{CT10PDF} & A14 & NLO \\ \hline

Diboson & \multicolumn{2}{c|}{{\sherpa}~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & {\sherpa} & NLO/LO \\ \hline\hline
\end{tabular}
\label{mob}
\end{table}

### 2022-03-10 sections/strategy_Htautau.tex
update most comments

The analysis strategy adopted in the $\Htautau$ search is similar to the one used in Ref.~\cite{fcnc36,Chen:2015nta} but extended to more search channels.
%\subsection{Event categorisation and kinematic reconstruction}
%\label{sec:htautau_reco_cat}
The $tt(qH)$ and $tH$ signal being probed are characterised by the presence of $\tau$-leptons from the decay of 
the Higgs boson, where the remaining top quark decays into $Wb$. There is an additional $q$-jet from the FCNC $t\to qH$ decay in the top pair production. 
%at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon, together with significant $\met$ is also expected.
In a significant fraction of the events, the lowest $\pt$ jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
resulting in only three reconstructed jets where the production mode is dominant. 
%some signal events mixed with production mode having only three reconstructed jets.
In order to optimise the sensitivity of the search, the selected events are categorised into seven SRs based on the number of light leptons,
$\had$ candidates, and on the number of light flavored jets:
$t_{\ell}\hadhad$, $t_{\ell}\had$-1j, $t_{\ell}\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}.

@@

%This event categorisation is primarily motivated by the different quality of the event kinematic reconstruction, depending on the amount 
%of $\met$ in the event (larger in $\lephad$ events compared with $\hadhad$ events), and whether a jet from the hadronic top-quark decay %is missing or not (events with exactly three jets or at least four jets).
This event categorisation is primarily motivated by optimizing the sensitivity in each signal region that targets either leptonic or hadronic top-quark
decays as well as the Higgs decays into either $\lephad$ or $\hadhad$ final states.   
The event kinematic reconstruction is used in the $t_h\hadhad$ and $t_h\lephad$ channels to suppress the background by constraining the
di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}.

@@

For the $t_ht(qH)$ events, the jet from $t\to qH$, denoted as the FCNC jet ($q$-jet), should be a hard narrow jet from the
decay chain $t\to qH\to q\tau\tau$, with taus reconstructed as $\lephad$ or $\hadhad$.
There should be at least four jets among which the one with the smaller angular distance to the visible decay of the di-tau,
is considered as the $q$-jet since the FCNC top decay products are likely boosted closer together than other jets. 
If there are more than two jets besides the $q$- and $b$-jet, the jets from $W$ boson decay are chosen from the combination
with the invariant mass closest to the $W$ boson mass. There is the chance that one of the jets fails the $\pt$ requirement and is not reconstructed.
This kind of events will fall into $t_hH$ final state.
%while the FCNC top resonance is
%still reconstructable that the missing jet is likely from the decay of $W$ boson.
%given the big chance that the jet which is missing is from $W$ decay.
There are three jets coming from top hadronic decay including the $b$-jet and a pair of opposite-sign $\had$ from the Higgs boson decay, where
both $t_h$ and $H$ can be reconstructed.  
%. So a Higgs resonance formed by the taus and a top resonance formed by
%the jets are expected.

The four-momenta of the invisible decay products from the decay of the $\tau$-leptons 
are estimated using a kinematics fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
measured $\met$ within their expected resolutions. The resolution on the Higgs boson mass is assumed to be $20~\gev$, while the resolution on the measured $\met$ is parameterised as a linear function of 
$\sqrt{\sum E_{\text{T}}}$, where $\sum E_{\text{T}}$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
After the $\chi^2$ minimisation, the Higgs boson $\pt$ as well as the 
$\pt$ of the parent top quarks are determined with better resolution in the signal events.

>>>>

The analysis strategy adopted in the $\Htautau$ search is similar to the one used in Ref.~\cite{fcnc36,Chen:2015nta} but extended to more search channels.
%\subsection{Event categorisation and kinematic reconstruction}
%\label{sec:htautau_reco_cat}
The $tt(qH)$ and $tH$ signal being probed are characterised by the presence of $\tau$-leptons from the decay of 
the Higgs boson, where the remaining top quark decays into $Wb$. There is an additional $q$-jet from the FCNC $t\to qH$ decay in the top pair production. 
%at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon, together with significant $\met$ is also expected.
In a significant fraction of the events, the lowest $\pt$ jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
resulting in only three reconstructed jets where the production mode is dominant. 
%some signal events mixed with production mode having only three reconstructed jets.
In order to optimise the sensitivity of the search, the selected events are categorised into seven signal regions(SRs) based on the number of light leptons,
$\had$ candidates, and on the number of light flavored jets:
%$t_{\ell}\hadhad$, $t_{\ell}\had$(1j and 2j), $t_{\ell}\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}. 
$t_{\ell}\hadhad$, $t_{\ell}\had$ (1j and 2j), $t_h\lephad$ (2j and 3j), $t_h\hadhad$ (2j and 3j), as shown in Table~\ref{tab:srcr}.

@@

%This event categorisation is primarily motivated by the different quality of the event kinematic reconstruction, depending on the amount 
%of $\met$ in the event (larger in $\lephad$ events compared with $\hadhad$ events), and whether a jet from the hadronic top-quark decay %is missing or not (events with exactly three jets or at least four jets).
This event categorisation is primarily motivated by optimizing the sensitivity in each signal region that targets either leptonic or hadronic top-quark
decays as well as the Higgs decays into either $\lephad$ or $\hadhad$ final states.   
%The event kinematic reconstruction is used in the $t_h\hadhad$ and $t_h\lephad$ channels to suppress the background by constraining the di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}.
The contribution of background to the signal regions $t_h\hadhad$ and $t_h\lephad$ channels is reduced by having a kinematic constraints on the di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}.

@@

For the $t_ht(qH)$ events, the jet from $t\to qH$, denoted as the FCNC jet ($q$-jet), should be a high $\pt$ jet from the
decay chain $t\to qH\to q\tau\tau$, with taus reconstructed as $\lephad$ or $\hadhad$.
%There should be at least four jets among which the one with the smaller angular distance to the visible decay of the di-tau,
%is considered as the $q$-jet 
Events should contain 4 jets, with the one at the smallest angular distance to the visible decay of the di-tau being labelled as the q-jet since the FCNC top decay products are likely boosted closer together than other jets. 
If there are more than two jets besides the $q$- and $b$-jet, the jets from $W$ boson decay are chosen from the combination
with the invariant mass closest to the $W$ boson mass. There is the chance that one of the jets fails the $\pt$ requirement and is not reconstructed.
These kinds of events will fall into $t_hH$ final state.
%while the FCNC top resonance is
%still reconstructable that the missing jet is likely from the decay of $W$ boson.
%given the big chance that the jet which is missing is from $W$ decay.
There are three jets coming from top hadronic decay including the $b$-jet and a pair of opposite-sign $\had$ from the Higgs boson decay, where
both $t_h$ and $H$ can be reconstructed.  
%. So a Higgs resonance formed by the taus and a top resonance formed by
%the jets are expected.

The four-momenta of the invisible decay products from the decay of the $\tau$-leptons 
are estimated using a kinematic fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
measured $\met$ within their expected resolutions. The resolution on the Higgs boson mass is assumed to be $20~\gev$, while the resolution on the measured $\met$ is parameterised as a linear function of 
$\sqrt{\sum E_{\text{T}}}$, where $\sum E_{\text{T}}$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
After the $\chi^2$ minimisation, the Higgs boson $\pt$ as well as the 
$\pt$ of the parent top quarks are determined with better resolution in the signal events.

### 2022-03-10 sections/systematic_uncertainties.tex
updating to V0.5
update most comments

Several sources of systematic uncertainty that can affect the normalisation of signal 
and background and/or the shape of their corresponding discriminant distributions are considered.
Each source is considered to be uncorrelated with the other sources.  
Correlations of a given systematic uncertainty are maintained across processes and channels 
as appropriate.
The following sections describe the systematic uncertainties considered.

@@

The uncertainty on the pileup reweighing is evaluated by varying the pileup scale factors
by 1$\sigma$ based on the reweighing of the average interactions per bunch crossing. However, this
uncertainty is highly correlated with the luminosity uncertainty and may be an overestimate.

>>>>

Several sources of systematic uncertainty that can affect the normalisation of signal 
and background and/or the shape of their corresponding discriminant distributions are considered.
Each source is considered to be uncorrelated with the other sources.  
Correlations of a given systematic uncertainty are maintained across processes and channels 
as appropriate. The following sections describe the systematic uncertainties considered.
Table~\ref{tab:had_sys_impact} shows a summary of the dominant systematics uncertainties on the measured $\BR(H\to qH)$ branching ratio
resulting from the fits to the data in the signal regions as described in Section~\ref{sec:result}.

@@

%The uncertainty on the pileup reweighing is evaluated by varying the pileup scale factors by 1$\sigma$ based on the reweighing of the average interactions per bunch crossing. However, this uncertainty is highly correlated with the luminosity uncertainty and may be an overestimate.
Scale factors are applied to reweight simulated events in order to obtain the pile-up distribution corresponding to data. An uncertainty on these reweighting scale factors is considered based on the disagreement between the instantaneous luminosity in data and in simulation.
